Robust Control of a Fluxonium Qubit

### 2021-01-12 paper/1introduction.tex
majority of jens and colm comments adressed

\section{Introduction}
Quantum optimal control (QOC) techniques are a class of optimization
algorithms for accurately and efficiently manipulating quantum systems.
Early techniques were proposed for nuclear magnetic resonance experiments
\cite{vandersypen2005nmr, kehlet2004improving, khaneja2005optimal,
  maximov2008optimal, nielsen2010optimal, skinner2003application, tosner2009optimal},
and applications now include superconducting circuits \cite{abdelhafez2020universal,
  chakram2020multimode, fisher2010optimal, gokhale2019partial,
  huang2020engineering, leng2019robust, leung2017speedup, li2020fast,
  xu2020nonadiabatic},
neutral atoms and ions \cite{brouzos2015quantum,
  de2008optimal, goerz2011quantum, guo2019high, jensen2019time,
  larrouy2020fast, omran2019generation, rosi2013fast, sorensen2019qengine,
  treutlein2006microwave, van2016optimal},
nitrogen-vacancy centers in diamond \cite{chou2015optimal,
  dolde2014high, geng2016experimental,
  nobauer2015smooth, poggiali2018optimal, rembold2020introduction, tian2019optimal},
and Bose-Einstien condensates \cite{amri2019optimal, sorensen2018quantum}.
For quantum computation,
optimal control techniques are employed to achieve high fidelity gates
while adhering to experimental constraints.
Experimental errors may cause the system to deviate
from the model used in optimization, leading
to poor experimental performance.
Robust control techniques improve upon
standard optimal control techniques by encoding
model uncertainties
in optimization objectives, yielding performance
guarantees over a range of parameters \cite{Zhou97,Morimoto00,Manchester18}.
We adapt robust control techniques from the robotics community to mitigate
parameter deviation errors for
a superconducting fluxonium qubit.

QOC techniques have had tremendous success in
engineering high fidelity quantum gates \cite{
  chou2015optimal, dolde2014high, egger2013optimized, egger2014adaptive,
  grace2007optimal, heeres2017implementing, huang2014optimal,
  kelly2014optimal, leng2019robust, liebermann2016optimal,
  nebendahl2009optimal, rebentrost2009optimal, rebentrost2009optimal2,
  spiteri2018quantum, sporl2007optimal}. 
While standard QOC techniques can predict system behavior
with high accuracy, they are sensitive to experimental
errors such as parameter drift, noise, finite control 
resolution, and decoherence. Multiple techniques have been developed to address
these shortcomings. Analytic techniques to mitigate parameter deviation errors
include composite pulses \cite{cummins2000use, cummins2003tackling,
  kupce1995stretched, merrill2014progress},
dynamic and geometric phase considerations
\cite{han2020experimental, xu2020nonadiabatic},
and the DRAG scheme \cite{motzoi2009simple}.
To mitigate decoherence, Floquet techniques have been employed
\cite{huang2020engineering, mundada2020floquet}.
Numerical techniques to mitigate parameter deviation errors
include closed-loop methods \cite{egger2014adaptive, feng2018gradient, huang2020engineering,
  wittler2020integrated} and open-loop methods \cite{
  allen2019robust, carvalho2020error, reinhold2019controlling,
  rembold2020introduction, kosut2013robust}.
Numerical techniques to mitigate decoherence include
modeling master equations \cite{rembold2020introduction} and employing
Monte Carlo style quantum trajectories \cite{abdelhafez2019gradient}.

In this work, we study three robust control techniques that
make the system's state trajectory less sensitive
to static and time-dependent parameter deviations:
\begin{enumerate}
  \item A sampling method, similar to the work of \cite{allen2019robust,
    carvalho2020error, reinhold2019controlling, rembold2020introduction}.
  \item An unscented sampling method adapted from the unscented transform used in the 
    state estimation community \cite{howell2020direct, julier2004unscented,
      lee2013sigma, manchester2016derivative}.
  \item A derivative-penalization method, which uses efficient mixed-mode differentiation
    to compute the sensitivity of the quantum state trajectory
    to deviant parameters.
\end{enumerate}
We apply these techniques to the fluxonium qubit presented in \cite{zhang2020universal}.
We also show that QOC can solve important problems for fluxonium-based qubits: mitigating
longitudinal relaxation type decoherence
by taking advantage of the $T_{1}$-dependence of the controls
and performing phase gates in arbitrary times.
To mitigate errors due to longitudinal
relaxation, we perform time-optimal control and
utilize an efficient optimization objective that does
not pay the increased computational cost of integrating a master equation.
Leveraging recent advances in trajectory optimization within the field of robotics, we
solve these optimization problems using the ALTRO solver, which uses iterative LQR 
(iLQR)---a differential-dynamic programming (DDP)-based indirect method similar to shooting
methods such as GOAT \cite{machnes2015gradient}, GRAPE
\cite{khaneja2005optimal, leung2017speedup}, and Krotov's \cite{goerz2019krotov}---within 
an augmented Lagrangian framework to handle nonlinear equality and inequality constraints at 
each time step \cite{howell2019altro}.

This paper is organized as follows.
First, we introduce the ALTRO method in the context of QOC
in Section \ref{sec:background}.
We describe realistic constraints for the fluxonium and
map them to the ALTRO method in Section \ref{sec:fluxonium}. Then, we
outline a method for making the optimization aware of longitudinal
relaxation in Section \ref{sec:longitude}. Next, we outline three methods for achieving
robustness to static parameter deviations in Section \ref{sec:static}. Finally,
we employ the robust control techniques to mitigate 1/$f$ flux noise
in Section \ref{sec:stochastic}.

>>>>

\section{Introduction}
Quantum optimal control (QOC) is a class of optimization
algorithms for accurately and efficiently manipulating quantum systems.
Early techniques were proposed for nuclear magnetic resonance experiments
\cite{vandersypen2005nmr, kehlet2004improving, khaneja2005optimal,
  maximov2008optimal, nielsen2010optimal, skinner2003application, tosner2009optimal},
and applications now include superconducting circuits \cite{abdelhafez2020universal,
  chakram2020multimode, fisher2010optimal, gokhale2019partial,
  huang2020engineering, leng2019robust, leung2017speedup, li2020fast,
  xu2020nonadiabatic},
neutral atoms and ions \cite{brouzos2015quantum,
  de2008optimal, goerz2011quantum, guo2019high, jensen2019time,
  larrouy2020fast, omran2019generation, rosi2013fast, sorensen2019qengine,
  treutlein2006microwave, van2016optimal},
nitrogen-vacancy centers in diamond \cite{chou2015optimal,
  dolde2014high, geng2016experimental,
  nobauer2015smooth, poggiali2018optimal, rembold2020introduction, tian2019optimal},
and Bose-Einstein condensates \cite{amri2019optimal, sorensen2018quantum}.
For quantum computation,
optimal control is employed to achieve high-fidelity gates
while adhering to experimental constraints.
Experimental errors may cause the system to deviate
from the model used in optimization, leading
to poor experimental performance.
Robust control improves upon
standard optimal control by encoding
model parameter uncertainties
in optimization objectives, yielding performance
guarantees over a range of parameter values \cite{Zhou97,Morimoto00,Manchester18}.
We adapt robust control techniques from the robotics community to mitigate
parameter uncertainty errors for
a superconducting fluxonium qubit.

QOC has had tremendous success in
engineering high-fidelity quantum gates \cite{
  chou2015optimal, dolde2014high, egger2013optimized, egger2014adaptive,
  grace2007optimal, heeres2017implementing, huang2014optimal,
  kelly2014optimal, leng2019robust, liebermann2016optimal,
  nebendahl2009optimal, rebentrost2009optimal, rebentrost2009optimal2,
  spiteri2018quantum, sporl2007optimal}. 
However, the system often
deviates from the model used in optimization
due to experimental errors such as parameter drift, noise, finite control 
resolution, and decoherence. Multiple techniques have been
developed to address this shortcoming.
Analytically-derived control pulses that
mitigate parameter uncertainty errors include
composite pulses \cite{cummins2000use, cummins2003tackling,
  kupce1995stretched, merrill2014progress},
pulses designed by considering dynamic and geometric phases
\cite{han2020experimental, xu2020nonadiabatic}, and
pulses obtained with the DRAG scheme \cite{motzoi2009simple}.
To suppress decoherence, Floquet techniques have been employed
\cite{huang2020engineering, mundada2020floquet}.
Numerical schemes to mitigate parameter uncertainty errors
include closed-loop methods \cite{egger2014adaptive, feng2018gradient,
  wittler2020integrated} and open-loop methods \cite{
  allen2019robust, carvalho2020error, reinhold2019controlling,
  rembold2020introduction, kosut2013robust}.
To model decoherence, numerical techniques typically employ
master equations \cite{rembold2020introduction, schulteherbruggen2011optimal} or
Monte Carlo-style quantum trajectories \cite{abdelhafez2019gradient}.

In this work, we study three robust control techniques that
make the system's quantum state trajectory less sensitive
to static and time-dependent parameter uncertainty:
\begin{enumerate}
  \item A sampling method, similar to the work of \cite{allen2019robust,
    carvalho2020error, khaneja2005optimal, reinhold2019controlling, rembold2020introduction}.
  \item An unscented sampling method adapted from the unscented transform used in
    state estimation \cite{howell2020direct, julier2004unscented,
      lee2013sigma, manchester2016derivative}.
  \item A derivative method, which penalizes the sensitivity of the quantum state trajectory
    to uncertain parameters.
\end{enumerate}
We apply these techniques to the fluxonium qubit presented in \cite{zhang2020universal}.
We also show that QOC can solve important problems associated with
fluxonium-based qubits: mitigating
depolarization by taking advantage of the $T_{1}$-dependence of the controls
and synchronizing qubits with distinct frequencies
by performing phase gates in arbitrary times.
To mitigate depolarization,
we perform time-optimal control and
employ an efficient depolarization model that 
is significantly less expensive to compute than integrating a master equation.
Leveraging recent advances in trajectory optimization within the field of robotics, we
solve these optimization problems using ALTRO (Augmented Lagrangian TRajectory Optimizer)
\cite{howell2019altro}, which uses the iterative linear quadratic regulator (iLQR) method
\cite{Li2004a} within an augmented Lagrangian framework \cite{lantoine2012hybrid,
  plancher2017constrained}
to handle nonlinear equality and inequality constraints at 
each time step.

This paper is organized as follows.
First, we reintroduce ALTRO in the context of QOC
in Section \ref{sec:background}.
We describe realistic constraints for operating the fluxonium and
define the associated QOC problem in Section \ref{sec:fluxonium}.
Then, we outline a method for making the optimization aware of depolarization
in Section \ref{sec:longitude}. Next, we outline three techniques for achieving
robustness to static parameter uncertainties in Section \ref{sec:static}. We
adapt the same techniques to mitigate 1/$f$ flux noise
in Section \ref{sec:stochastic}.

### 2021-01-12 paper/3fluxonium.tex
small constraint updates
more minor constraint updates
majority of jens and colm comments adressed

\section{QOC on the Fluxonium \label{sec:fluxonium}}
In the following, we study
the QOC problem on the fluxonium qubit.
The fluxonium qubit is a promising building block for superconducting
circuits, and the accurate
two-level approximation of its Hamiltonian makes
QOC on a classical computer inexpensive.
In the two-level
approximation the Hamiltonian takes the form:
\begin{align}
  H/h &= f_{q} \frac{\sigma_{z}}{2} + a(t) \frac{\sigma_{x}}{2}
  \label{eq:hamiltonian}
\end{align}
where $f_{q} = 14$MHz is the qubit frequency at the flux frustration point,
$a(t)$ is the flux drive amplitude, $h$ is Planck's constant, and $\sigma_{x}, \sigma_{y}$
are Pauli matrices. We consider the task of constructing $Z/2$, $Y/2$, and $X/2$
gates for the fluxonium qubit subject to experimental constraints, decoherence, and
Hamiltonian parameter deviations. We compare the gates we obtain with numerical
methods to the analytically constructed gates reported in
\cite{zhang2020universal} for the same device.

The optimization problem takes the form:
\begin{mini!}[2] 
  {x_{1:N}, u_{1:N\text{-}1}}{\sum_{k=1}^N \norm{x_k\text{-}x_f}_{Q_k}
    + \sum_{k=1}^{N-1} \norm{u_k}_{R_k}}{}{} \label{eq:costfun}
  \addConstraint{x_{k+1}}{= f(x_k, u_k)}  \label{eq:dyn_con}
  \addConstraint{\ket{\psi^{0}_{1}} = \ket{0}, \ket{\psi^{1}_{1}} = \ket{1}} \label{eq:istate_con}
  \addConstraint{\ket{\psi^{i}_{N}} = \ket{\psi^{i}_{f}}} \label{eq:tstate_con}
  \addConstraint{{\lvert \braket{\psi^{i}_{k}}{\psi^{i}_{k}}
      \rvert}^{2} = 1} \label{eq:statenorm_con}
  \addConstraint{{\textstyle \int^{t_{1}}_{0} a \ \mathrm{d}t} = \pdv*{a_{1}}{t} = 0}
  \label{eq:icintd_con}
  \addConstraint{{\textstyle \int^{t_{N}}_{0}} a \ \mathrm{d}t= 0} \label{eq:znf_con}
  \addConstraint{a_{1} = a_{N} = 0} \label{eq:concat_con}
  \addConstraint{|a_{k}| \leq 0.5 \ \textrm{GHz}} \label{eq:amp_con}
\end{mini!}
The augmented state and augmented controls are:
\begin{equation}
  x = \begin{bmatrix} \psi^{0} \\ \psi^{1} \\ \int^{t}_{0} a \ \mathrm{d}t\\ a \\ \pdv*{a}{t} \end{bmatrix} \quad
  u = \begin{bmatrix} \pdv*[2]{a}{t} \end{bmatrix}
  \label{eq:astatecontrols}
\end{equation}
The matrices $Q_{k}$ and $R_{k}$ define the penalty metric.
Including objectives at each knot point smoothens the optimization landscape, though
the importance of the final objective is encoded in the relative
weight $Q_{N} \sim N \cdot Q_{k}$.
We choose $Q$ to be diagonal because it is computationally efficient. This
metric penalizes phase differences between the states, although
phase-insensitive metrics such as infidelity may be employed.

We impose constraints that
reflect the physical limitations of the apparatus and 
improve the experimental realization of the control pulse.
The discrete dynamics \eqref{eq:dyn_con} integrates the states
according to the TDSE \eqref{eq:tdse} and the
fluxonium Hamiltonian \eqref{eq:hamiltonian}
and integrates the moments of the flux amplitude.
Exposing lower order moments of the flux amplitude allows us to penalize their norms
in \eqref{eq:costfun}, smoothing the flux amplitude
and mitigating AWG ringing due to high frequency transitions.
We ensure the desired gate is achieved by imposing the constraints
\eqref{eq:istate_con} and \eqref{eq:tstate_con}.
The initial states in \eqref{eq:istate_con}
are chosen to span the Hilbert space.
The final states in \eqref{eq:tstate_con} are the image
of the initial states under the desired gate.
The ALTRO implementation we use does not currently support complex numbers so
we compute in the isomorphism $\mathcal{H}(\mathbb{C}^{n}) \cong \mathcal{H}(\mathbb{R}^{2n})$
given in \cite{leung2017speedup},
\begin{equation}
  H \ket{\psi} \cong \begin{bmatrix} H_{\textrm{re}} & -H_{\textrm{im}}
    \\ H_{\textrm{im}} & H_{\textrm{re}}\end{bmatrix}
  \begin{bmatrix} \psi_{\textrm{re}} \\ \psi_{\textrm{im}}\end{bmatrix}
  \label{eq:isomorphism}
\end{equation}
We ensure the solver does not take advantage of discretization
error by imposing the normalization constraint \eqref{eq:statenorm_con}.
The constraint \eqref{eq:icintd_con} is an initial condition.
We ensure the pulse has zero net flux by imposing \eqref{eq:znf_con},
which mitigates the hysteresis ubiquitous in flux bias lines
\cite{battistel2019fast, krantz2019quantum, zhang2020universal}.
We ensure gates may be concatenated arbitrarily without
inducing AWG ringing due to high-frequency transitions by imposing
the boundary condition \eqref{eq:concat_con}.
Finally, we ensure the two-level
approximation \eqref{eq:hamiltonian} remains valid
by imposing the amplitude constraint \eqref{eq:amp_con}.
All of the gates presented in this work achieve a maximum
individual constraint violation of $10^{-8}$
for \eqref{eq:dyn_con}--\eqref{eq:amp_con}.

>>>>

\section{QOC for the Fluxonium \label{sec:fluxonium}}
In the following, we optimize quantum gates
(unitary transformations) for the fluxonium qubit.
The fluxonium is a promising building block
for quantum computers, and the accurate
two-level approximation of its Hamiltonian makes
QOC on a classical computer inexpensive.
In the two-level
approximation, the Hamiltonian takes the form:
\begin{align}
  H/h &= f_{q} \frac{\sigma_{z}}{2} + a(t) \frac{\sigma_{x}}{2}
  \label{eq:hamiltonian}
\end{align}
where $f_{q}$ is the qubit frequency at the flux frustration point,
$a(t)$ is the flux-drive amplitude, $h$ is Planck's constant, and $\sigma_{z}, \sigma_{x}$
are Pauli matrices. We optimize $X/2$, $Y/2$, and
$Z/2$ gates for the fluxonium presented in \cite{zhang2020universal},
and compare them to the analytically constructed gates for
that device.

First, we outline the constraints for the fluxonium gate problem.
We formulate this problem as a multi-state-transfer problem.
The initial conditions on
the states are $\ket{\psi^{0}_{1}} = \ket{0}$, $\ket{\psi^{1}_{1}} = \ket{1}$
\eqref{eq:istate_con}
where the superscript is an index $i \in \{0, 1\}$,
and the subscript indicates the first knot point $k = 1$.
The states at the final knot point are constrained to be
the image of the initial states under the desired gate $U$,
$\ket{\psi^{i}_{N}} = U \ket{\psi^{i}_{1}} \ \forall \ i$
\eqref{eq:tstate_con}.
%% This constraint is sensitive to global phase
%% differences between the states.
%% , but it is computationally efficient
%% because the Jacobian and Hessian
%% of the corresponding constraint function are diagonal.
%% We could have analogously chosen a metric which is insensitive
%% to global phases, such as the fidelity of the states.
Furthermore, we impose the normalization constraint
${\lvert \braket{\psi^{i}_{k}}{\psi^{i}_{k}} \rvert}^{2} = 1 \ \forall \ i,k$
\eqref{eq:statenorm_con}
to ensure the solver does not take advantge of discretization errors in numerical integration.
To refer to the discrete moments the flux amplitude, we introduce the notation
$\int^{t_{k}}_{t_{1}} a(t) \ \mathrm{d}t \equiv \int_{t} a_{k}$,
$a(t) \lvert_{t = t_{k}} \equiv a_{k}$,
$\pdv*[n]{a(t)}{t} \lvert_{t = t_{k}} \equiv \partial^{n}_{t} a_{k}$.
We impose the zero net flux constraint $\int_{t} a_{N} = 0$
\eqref{eq:znf_con}
which mitigates the hysteresis ubiquitous in flux-bias lines
\cite{battistel2019fast, krantz2019quantum, zhang2020universal}.
The flux amplitude is constrained by $\lvert a_{k} \rvert \leq 0.5 \ \textrm{GHz} \ \forall \ k$
\eqref{eq:amp_con}
to ensure the two-level approximation \eqref{eq:hamiltonian} remains valid.
We also enforce the boundary condition $a_{1} = a_{N} = 0$ \eqref{eq:bound_con}
so the gates may be concatenated arbitrarily. Additionally,
we have the initial condition $\int_{t} a_{1} = \partial_{t} a_{1} = 0$
\eqref{eq:ic_con}.

%% F1
\begin{figure*}[ht]

  \begin{subfigure}{.315\textwidth}
    \includegraphics[width=\linewidth]{assets/f1a.png}
    \caption{\label{fig:longitudea}}
  \end{subfigure}\hfill
  \begin{subfigure}{.23\textwidth}
    \includegraphics[width=\linewidth]{assets/f1b.png}
    \caption{\label{fig:longitudeb}}
  \end{subfigure}\hfill
  \begin{subfigure}{.4\textwidth}
    \includegraphics[width=\linewidth]{assets/f1c.png}
    \caption{\label{fig:longitudec}}
  \end{subfigure}
  \caption{
    (a) Numerically optimized gates (dark blue)
    and analytically optimized gates (light pink).
    (b) $T_{1}$ interpolation function used in optimization. Markers
    denote the time-averaged, absolute amplitude of each gate.
    (c) Cumulative gate errors due to depolarization as a function of the
    number of gates applied.
    Gate errors for the numerically optimized $Z/2$ and $Y/2$ gates
    are indistinguishable. Inset shows the cumulative gate errors
    plotted on a log scale for small gate counts.
  }
  \label{fig:longitude}
\end{figure*}

Next, we outline the cost functions for the fluxonium gate problem.
The augmented state and augmented control are:
\begin{equation}
  \begingroup
  \renewcommand*{\arraystretch}{1.3}
  x_{k} = \begin{bmatrix} \ket{\psi^{0}_{k}} \\ \ket{\psi^{1}_{k}}
    \\ \int_{t} a_{k} \\ a_{k} \\ \partial_{t} a_{k} \end{bmatrix} \quad
  u_{k} = \begin{bmatrix} \partial^{2}_{t} a_{k} \end{bmatrix}
  \endgroup
  \label{eq:astatecontrols}
\end{equation}
The cost function at each knot point is
$\ell_{k}(x_{k}, u_{k}) = (x_{k} - x_{f})^{T} Q_{k} (x_{k} - x_{f}) + u^{T}_{k} R_{k} u_{k}$
where $Q_{k}$ and $R_{k}$ are matrices we supply, and
$x_{f}$ is given by the constraints we have imposed on
$\ket{\psi^{i}_{N}}$, $\int_{t} a_{N}$, and $a_{N}$ in addition to
$\partial_{t} a_{f} = 0$. We choose $Q_{k}$ to be diagonal
so the cost function incentivizes the achievement of the constraints on
$\ket{\psi^{i}_{N}}$, $\int_{t} a_{N}$, and $a_{N}$,
and penalizes the norm of $\partial_{t} a_{k}$ and $\partial^{2}_{t} a_{k}$,
mitigating AWG ringing due to high-frequency transitions.
In the discrete dynamics function for this problem \eqref{eq:dyn_con},
we integrate the states according to the TDSE \eqref{eq:tdse} and the
fluxonium Hamiltonian \eqref{eq:hamiltonian} and integrate
the second-derivative of the flux amplitude to obtain
the first-derivative, proportional, and integral moments.
Stated succinctly, the optimization problem takes the form:
\begin{mini!}[2] 
  {x_{1:N}, u_{1:N\text{-}1}}{\sum_{k=1}^N {(x_k\text{-}x_f)}^{T} Q_k (x_k\text{-}x_{f})
    + \sum_{k=1}^{N-1} {u_k}^{T} R_k u_{k}}{}{} \label{eq:costfun}
  \addConstraint{x_{k+1}}{= f(x_k, u_k)}  \label{eq:dyn_con}
  \addConstraint{\ket{\psi^{0}_{1}} = \ket{0}, \ket{\psi^{1}_{1}} = \ket{1}} \label{eq:istate_con}
  \addConstraint{\ket{\psi^{i}_{N}} = U \ket{\psi^{i}_{1}}
    \ \forall \  i} \label{eq:tstate_con}
  \addConstraint{{\lvert \braket{\psi^{i}_{k}}{\psi^{i}_{k}}
      \rvert}^{2} = 1 \ \forall \ i, k} \label{eq:statenorm_con}
  \addConstraint{{\textstyle \int_{t}} a_{N} = 0} \label{eq:znf_con}
  \addConstraint{|a_{k}| \leq 0.5 \ \textrm{GHz} \ \forall \ k} \label{eq:amp_con}
  \addConstraint{a_{1} = a_{N} = 0} \label{eq:bound_con}
  \addConstraint{{\textstyle \int_{t}} a_{1} = \partial_{t} a_{1} = 0} \label{eq:ic_con}
\end{mini!}

### 2021-01-12 paper/6stochastic.tex
added constraints to opt statement
majority of jens and colm comments adressed

\section{Robustness to Time-Dependent Parameter Deviations \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
Hamiltonian parameter deviations. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is a significant
source of coherent errors. Magnetic flux noise
modifies the fluxonium Hamiltonian \eqref{eq:hamiltonian}
by $a(t) \gets a(t) + \delta a(t)$.
The spectral density of $\delta a(t)$ follows a
1/$f$ distribution for a range of devices, consisting primarily of low frequency
noise \cite{bialczak20071f, koch2007model,
  yoshihara2006decoherence, yoshihara2010correlated}.
Analytic methods to combat flux noise
take advantage of the low-frequency characteristic and
treat the noise as quasi-static, performing generalizations of the spin-echo technique
to compensate for erroneous drift. The analytic gate considered here
follows this strategy.

We challenge the analytic method and
the robust control
methods of the previous section
to realize an $X/2$ gate subject to 1/$f$ flux noise.
We compute gate errors for each method
by evolving the system under the Hamiltonian in \eqref{eq:hamiltonian}
where the optimized flux amplitude is modified $a(t) \gets a(t) + \delta a(t)$.
The flux noise $\delta a(t)$ is generated by
filtering white noise sampled from a standard normal distribution with a finite
impulse response filter \cite{saspweb2011}.
It is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\delta a (t) \sim \sigma_{a} = 2.5 \cdot 10^{-5} \textrm{GHz}$.
The unscented sampling method is modified so that its samples
are subject to 1/$f$ flux noise by carrying the state of a finite impulse response filter
in the augmented state vector \eqref{eq:astatecontrols}.
In principle, we could modify the sampling method
similarly; however, we choose to sample statically at $\sigma_{a}$ for comparison.
The derivative methods require no algorithmic modification from the static case,
but the TDSE is now differentiated with respect to $a(t)$ instead of $f_{q}$ as
in \eqref{eq:d1dyn}.

We simulate successive applications of the gate constructed by each method
and compute the cumulative gate error
after each application, see Figure \ref{fig:stochastic}.
Both the analytic
and numerical methods achieve single gate errors
sufficient for quantum error correction.
Despite converging on qualitatively different solutions, the
numerical methods perform similarly in the concatenated
gate application comparison. They achieve a two
order of magnitude cumulative gate error reduction over the analytic method after $200$
gate applications $\sim 11 \mu\textrm{s}$.
1/$f$ flux noise is a significiant source of coherent errors in NISQ applications and
these numerical techniques offer effective avenues to mitigate it.

>>>>

\section{Robustness to Time-Dependent Parameter Uncertainty \label{sec:stochastic}}
An additional source of experimental error arises from time-dependent
Hamiltonian parameter uncertainty. For many flux-biased and inductively-coupled
superconducting circuit elements, magnetic flux noise is a significant
source of coherent errors \todo{coherent errors?}. Flux noise
modifies the fluxonium Hamiltonian \eqref{eq:hamiltonian}
by $a(t) \rightarrow a(t) + \delta a(t)$.
The spectral density of flux noise is known to
follow a 1/$f$ distribution
\cite{bialczak20071f, koch2007model,
  yoshihara2006decoherence, yoshihara2010correlated},
so the noise is dominated by low-frequency components.
The analytic gate considered here
takes advantage of the low-frequency characteristic and
treat the noise as quasi-static, performing a generalization of the spin-echo
technique to compensate for erroneous drift.

Additionally, we modify the robust control techniques presented
in the previous section to combat 1/$f$ flux noise.
The unscented sampling method is modified so that the sample states
are subject to 1/$f$ flux noise. The noise
is generated by filtering white noise sampled from a standard
normal distribution with a finite impulse response filter \cite{saspweb2011}.
The noise is then scaled by the 
flux noise amplitude of our device $A_{\Phi} = 5.21 \mu \Phi_{0} \implies
\sigma_{a} = 2.5 \cdot 10^{-5} \textrm{GHz}$.
In principle, we could modify the sampling method
similarly; however, we choose to sample statically $a(t) \rightarrow a(t) + \sigma_{a}$
for comparison. The derivative methods require no algorithmic modification
from the static case, but the TDSE is now differentiated with respect
to $a(t)$ instead of $f_{q}$ as in \eqref{eq:d1dyn}.

We compare the gate errors due to 1/$f$ flux noise for $X/2$
gates constructed with the robust control techniques
and the analytic method. To compute the gate error,
an initial state is evolved
under the fluxonium Hamiltonian \eqref{eq:hamiltonian}
where the optimized flux amplitude is modified $a(t) \rightarrow a(t) + \delta a(t)$.
The flux noise $\delta a(t)$ is generated as
we described for the unscented sampling method.
Each of the $1000$ averages we perform uses a different random seed for
generating the flux noise.
We simulate successive applications of the gate constructed by each method
and compute the cumulative gate error
after each application, see Figure \ref{fig:stochastic}.
Both the analytic
and numerical gates yield single gate errors
sufficient for quantum error correction.
Despite converging on qualitatively different solutions, the
numerical gates perform similarly in the concatenated
gate application comparison. Their gate errors
after $200$ gate applications $\sim 11 \mu\textrm{s}$ are
two orders of magnitude less than the gate error produced by the analytic gate.
\todo{motional narrowing}.
1/$f$ flux noise is a significiant source of coherent errors in NISQ applications and
these numerical techniques offer effective avenues to mitigate it.

### 2021-01-12 paper/7conclusion.tex
majority of jens and colm comments adressed

\section{Conclusion}
In conclusion, we have applied state-of-the-art trajectory
optimization techniques to achieve robustness to parameter deviations
and mitigate decoherence on a quantum system.
We have proposed a scheme for mitigating
longitudinal relaxation with time-optimal
control and the probability of longitudinal relaxation metric,
avoiding the optimal control problem for density matrices which scales quartically with
the dimension of the Hilbert space.
We have proposed the derivative method for robust control which achieves
super-linear gate error reductions in its gate time for the static parameter
deviation problem we studied.
We have shown that the derivative, sampling, and unscented sampling methods
can mitigate 1/$f$ flux noise errors
which dominate coherent errors for flux controlled qubits.
The derivative and sampling methods scale cubically with
the dimension of the Hilbert space, allowing for applications
to larger quantum systems.
The derivative, sampling, and unscented sampling
methods will benefit from interleaving optimization with
experimental characterization, while the sampling and unscented
sampling methods can also be applied to error channels without models.
These techniques will be used to achieve the low gate errors
required for fault-tolerant quantum computing applications. Our
implementation of the techniques described in this work is available
at \url{https://github.com/SchusterLab/rbqoc}.

>>>>

\section{Conclusion}
In conclusion, we have applied state-of-the-art trajectory
optimization techniques to mitigate decoherence and
achieve robustness to parameter uncertainty
errors on a quantum system.
We have proposed a scheme for supressing
depolarization with time-optimal
control and the depolarization probability model.
The computational cost of this depolarization model is
independent of the dimension of the Hilbert space, enabling
inexpensive optimization on high-dimensional quantum systems.
We have also proposed the derivative method for robust control which achieves
super-linear gate error reductions in the gate time for the static parameter
uncertainty problem we studied.
We have shown that the derivative, sampling, and unscented sampling methods
can mitigate 1/$f$ flux noise errors
which dominate coherent errors for flux controlled qubits.
The robust control techniques can be applied
to any Hamiltonian,
allowing experimentalists in all disciplines to engineer robust
operations on their quantum systems.
These methods will be used to achieve the low gate errors
required for fault-tolerant quantum computing applications. Our
implementation of the techniques described in this work is available
at \url{https://github.com/SchusterLab/rbqoc}.
